---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# erpcore

The goal of `erpcore` is to provide some simple command line functions for downloading the ERP CORE datasets (Kappenman, Farrens, Zhang, Stewart, & Luck, 2020) from the Open Science Framework website.

In their own words:

> The ERP CORE is a freely available online resource consisting of optimized paradigms, experiment control scripts, example data from 40 participants, data processing pipelines and analysis scripts, and a broad set of results for 7 different ERP components obtained from 6 different ERP paradigms:
>
> -   N170 (Face Perception Paradigm)
>
> -   MMN (Passive Auditory Oddball Paradigm)
>
> -   N2pc (Simple Visual Search Paradigm)
>
> -   N400 (Word Pair Judgement Paradigm)
>
> -   P3b (Active Visual Oddball Paradigm)
>
> -   LRP and ERN (Flankers Paradigm)

The ERP CORE is developed and maintained by

Kappenman, E., Farrens, J., Zhang, W., Stewart, A. X., & Luck, S. J. (2020). ERP CORE: An Open Resource for Human Event-Related Potential Research [Preprint]. PsyArXiv. <https://doi.org/10.31234/osf.io/4azqm>

For more information about the ERP CORE, visit [their website](https://erpinfo.org/erp-core).

You can also directly access the data at the [Open Science Framework website](https://doi.org/10.18115/D5JW4R)

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("craddm/erpcore")
```

## Usage

The `get_erpcore()` function can be used 

```{r eval = FALSE}
get_erpcore(component = "n170")
```

Or you can use one of the specific functions

```{r eval = FALSE}
get_n400(type = "bids")
```
